---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# enum

<!-- badges: start -->
<!-- badges: end -->

The `enum` package provides a robust implementation of enumerations (enums) for R, enabling the creation of type-safe, validated sets of named constants. Enums help prevent errors by constraining variables to predefined values and offer better code readability and maintainability.

## Installation

You can install the development version of enum from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("pak")
pak::pak("milanmlft/enum")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
# library(enum)

# # Create an enum for days of the week
# Days <- Enum(
#   MONDAY = 1,
#   TUESDAY = 2,
#   WEDNESDAY = 3,
#   THURSDAY = 4,
#   FRIDAY = 5,
#   SATURDAY = 6,
#   SUNDAY = 7
# )

# # Use the enum
# today <- Days$MONDAY
# today
```

## Features

- **Validation**: Values are automatically validated against defined constants
- **Readability**: Named constants make code more self-documenting
- **Maintainability**: Centralized definition of related constants

## Development

This package uses [pre-commit](https://pre-commit.com/) hooks to ensure code quality. To set up the development environment:

```bash
# Install pre-commit
pip install pre-commit

# Install the hooks
pre-commit install

# Run hooks manually
pre-commit run --all-files
```

## License

This project is licensed under the MIT License - see the [LICENSE](LICENSE) file for details.
