---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# enum

<!-- badges: start -->
[![R-CMD-check](https://github.com/milanmlft/enum/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/milanmlft/enum/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/milanmlft/enum/graph/badge.svg)](https://app.codecov.io/gh/milanmlft/enum)
[![pre-commit.ci status](https://results.pre-commit.ci/badge/github/milanmlft/enum/main.svg)](https://results.pre-commit.ci/latest/github/milanmlft/enum/main)
<!-- badges: end -->

The `enum` package provides a robust implementation of enumerations (enums) for R, enabling the creation of type-safe, validated sets of named constants. Enums help prevent errors by constraining variables to predefined values and offer better code readability and maintainability.

## Installation

You can install the development version of enum from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("pak")
pak::pak("milanmlft/enum")
```

## Example

```{r}
library(enum)

# Create an enum for days of the week
Days <- Enum(
  MONDAY = 1,
  TUESDAY = 2,
  WEDNESDAY = 3,
  THURSDAY = 4,
  FRIDAY = 5,
  SATURDAY = 6,
  SUNDAY = 7
)

# Use the enum
today <- Days$MONDAY
today
```

## Features

- **Validation**: Values are automatically validated against defined constants
- **Readability**: Named constants make code more self-documenting
- **Maintainability**: Centralized definition of related constants

### Accessors

Enums support the following accessors:

- `$`: Access a single value by name
- `[[`: Access multiple values by name
- `names`: Get the names of the enum

```{r}
Days[["MONDAY"]]
Days$TUESDAY
names(Days)
```

### Validation

All enum names must be unique and non-empty strings.

```{r, error = TRUE}
Days <- Enum(
  MONDAY = 1,
  MONDAY = 2
)
```

```{r, error = TRUE}
Days <- Enum(
  MONDAY = 1,
  2
)
```

### Immutability

Enums are immutable, meaning that once created, their values cannot be changed.

```{r, error = TRUE}
Days$MONDAY <- 8
```


## Development

This package uses [pre-commit](https://pre-commit.com/) hooks to ensure code quality. To set up the development environment:

```bash
# Install pre-commit
pip install pre-commit

# Install the hooks
pre-commit install

# Run hooks manually
pre-commit run --all-files
```

## License

This project is licensed under the MIT License - see the [LICENSE](LICENSE) file for details.
